---
title: "Favipiravir-resistant virus shows potential for transmission"
author: "Ada Yan"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{main}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Introduction

This vignette contains code to reproduce the modelling analysis and figures in the manuscript "Favipiravir-resistant virus shows potential for transmission", using data and functions in the `reassortment` package.

## Main text

```{r global_options, include=FALSE}
knitr::opts_chunk$set(eval = FALSE)
```

```{r}
library(reassortment)
```

```{r eval = TRUE, include = FALSE}
devtools::load_all()
```

`run_default_pars` is the function used to conduct simulations.

```{r}
run_default_pars(sim_name = "default")
```

runs model simulations for default parameter values, which are those for Fig. 3a in the manuscript, and Table 1 in the Appendix.
The results are saved in `results/default/results.rds` (the argument `sim_name` specifies the output folder).  The input parameter values (i.e. the default values in this case) are saved in `results/default/inputs.rds`.

`results.rds` contains a data frame:

```{r eval = TRUE}
results <- readRDS("results/default/results.rds")
head(results)
tail(results)
```

`run` is a integer from 1 to 100 (the number of stochastic simulations per scenario).  There are 20 rows for each run number. Rows number 1, 2, 3... for a given run number contain the proportions of each strain for generations 1, 2, 3... `MM`, `MW`, `WM` and `WW` are the double mutant, PB1 K229R, PA P653L, and WT respectively.

```{r eval = TRUE}
plot_multirun_strains(results)
```

plots Fig. 3A in the manuscript.

The optional arguments to `run_default_pars` change the default parameter values.

* `MOI`: multiplicity of infection (default 1)
* `iv`: initial proportion of each strain, in order of `MM, MW, WM, WW` (default `c(95,0,0,5)`)
* `fitness_MW`: fitness of PB1 K229R relative to WT (default 0.01)
* `fitness_WM`: fitness of PA P653L relative to WT (default 1.25)
* `fitness_MM`: fitness of PB1 K229R PA P653L relative to WT (default 1)
* `mutation_prob`: mutation probability per generation (default 2e-4)
* `reassort`: logical.  if `TRUE` (default), both reassortment and mutation occur; if `FALSE`, only mutation occurs
* `pop_size`: size of virus population (default 1e6)
* `burst size`: burst size per cell at MOI = 1 (default 10)
* `MOI_dependent_burst_size`: if `TRUE` (default), the burst size for a given cell scales linearly with the MOI for that cell; if `FALSE`, the burst size is independent of the MOI
* `choose_strain_by_fitness`: if `FALSE` (default), the strain composition of a cell's progeny is independent of strain fitness; if `TRUE`, the probability of each progeny being of a given strain is proportinal to its fitness

For example, to simulate Figs. 3B-D:

```{r}
run_default_pars(fitness_WM = 1, sim_name = "B")
run_default_pars(fitness_MW = 1, sim_name = "C")
run_default_pars(reassort = FALSE, sim_name = "D")
```

## Sensitivity analysis

Fig. 1

```{r}
# enumerate all combinations of fitness_WM and reassort
par_grid <- expand.grid(fitness_WM = c(1, 1.1, 1.5, 1.75, 2), reassort = c(FALSE, TRUE))
par_grid$sim_name <- paste0("fitness_WM_", num2str(par_grid$fitness_WM), "_", par_grid$reassort)
Map(run_default_pars, fitness_WM = par_grid$fitness_WM, 
    reassort = par_grid$reassort, sim_name = par_grid$sim_name)
```

Fig. 2
```{r}
par_grid <- expand.grid(fitness_MM = c(0.8, 0.9, 1.1, 1.2), reassort = c(FALSE, TRUE))
par_grid$sim_name <- paste0(n"fitness_MM_", um2str(par_grid$fitness_MM), "_", par_grid$reassort)
Map(run_default_pars, fitness_MM = par_grid$fitness_MM, 
    reassort = par_grid$reassort, sim_name = par_grid$sim_name)
```

Fig. 3

```{r}
par_grid <- expand.grid(mutation_prob = c(2e-3, 2e-5), reassort = c(FALSE, TRUE))
par_grid$sim_name <- paste0("mutation_prob_", num2str(par_grid$mutation_prob), "_", par_grid$reassort)
Map(run_default_pars, mutation_prob = par_grid$mutation_prob, 
    reassort = par_grid$reassort, sim_name = par_grid$sim_name)
```

Fig. 4

```{r}
par_grid <- expand.grid(MOI = .1, reassort = c(FALSE, TRUE))
par_grid$sim_name <- paste0("MOI_", num2str(par_grid$MOI), "_", par_grid$reassort)
Map(run_default_pars, MOI = par_grid$MOI, 
    reassort = par_grid$reassort, sim_name = par_grid$sim_name)
```

```{r}
par_grid <- expand.grid(MOI_dependent_burst_size = FALSE, reassort = c(FALSE, TRUE))
par_grid$sim_name <- paste0("MOI_dependent_burst_size_", par_grid$MOI_dependent_burst_size, "_", par_grid$reassort)
Map(run_default_pars, MOI_dependent_burst_size = par_grid$MOI_dependent_burst_size, 
    reassort = par_grid$reassort, par_grid$sim_name)
```

```{r}
par_grid <- expand.grid(choose_strain_by_fitness = TRUE, reassort = c(FALSE, TRUE))
par_grid$sim_name <- paste0("choose_strain_by_fitness_", par_grid$choose_strain_by_fitness, "_", par_grid$reassort)
Map(run_default_pars, choose_strain_by_fitness = par_grid$choose_strain_by_fitness, 
    reassort = par_grid$reassort, par_grid$sim_name)
```